\section{Educational events}
\label{sec:eduevent}
After the Tollgate, the analyst team had a lot of work ahead to complete and document relevant requirements and use cases. The lead analyst expressed this issue at the manager meeting on September 20th, which led to a workshop being planned to educate other people in the company to be able to create use cases to speed up the process. The workshop was open to anyone in the company to join.

The development workshop was planned for the purpose of getting everyone in the company set up with the development environment. This includes access to GitLab to be able to clone the project and get started working, set up Docker on everyone's computer, and educate all team members on how the code should be structured and how components should be created.

To get a good start with testing in the project, a workshop was planned where all the testers attended to synchronize their work and the tools that were going to be used. The different tools that were going to be used during the project were set up so that all testers had a working version and understood how to use it. Karma and Jasmine were evaluated in the workshop to see which framework was going to be the best to use in the project.

The GitLab workshop was planned with the intention of updating the company on how we should use GitLab and the tools it provides during the project. We previously used Trello for our issue needs, but it was discovered that GitLab provided this feature, together with many more tools useful for traceability as an example, which made us switch to GitLab to have everything in one place.

In the following table, any educational event (i.e., workshops) within the company will be listed, together with a short description of the event itself.

\begingroup
\begin{table}[ht]
    \renewcommand{\arraystretch}{1.5}
        \begin{tabular}{|M{3.5cm}|M{1cm}|M{2.5cm}|M{6cm}|}
        \hline
        \textbf{What} & \textbf{Date} & \textbf{Responsible} & \textbf{Description} \\
        \hline
        Analyst workshop & 24/9 & S. Andersson & Walk-through of creating use cases and finish creating use cases.\\
        \hline
         Development workshop & 28/9 & J. Karlén & Setting up the development environment and how to get started with development. \\
        \hline
         Testing workshop & 12/10 & A. Telenius & Workshop to evaluate and discuss test tools.\\
        \hline
         GitLab workshop & 3/11  & A. Ambrosius \& E. Sköld & Walk-through of guidelines and tools to use in GitLab. Focus points: requirements, labels, boards, workflow, commit messages, and merge requests.\\
        \hline
        \end{tabular}
\end{table}

\endgroup
%|c|c|c|c|